---
title: "Timepoints"
output: 
  html_document:
    css: "style.css"
---

# {.tabset .tabset-fade}  
## Example 1 - One Timepoint {-}  

<div class="row">
<div class="column">
<input
type="text"
placeholder="Search"
/>

<div style="border: 2px solid black; padding: 0 20px; margin-bottom: 20px; list-style-position: outside;">
<li>T1 (12/2019)</li>
<li>T2 (03/2020)</li>
<li>T3 (04/2020)</li>
<li>T4 (05/2020)</li>
<li>T5 (06/2020)</li>
<ul>
<li>Demographics</li>
<li>Job Attitudes</li>
<li>Ageing and Work</li>
<ul>
<li>Work Ability</li>
<li>Age Satisfaction</li>
<ul>
<li style="background:AliceBlue;">age_sat1: Things are getting worse as I get older</li>
<li>age_sat2: As you get older you are less useful</li>
<li>age_sat3: I have as much pep as I had last year</li>
<li>age_sat4: As I get older, things are better than I thought they would be</li>
<li>age_sat5: I am as happy now as when I was younger</li>
</ul>
</li>

</ul>
</li>

</ul>

</div>


#### Selection

<div style="border: 2px solid black; padding-left:5px;">age_sat1</div>  
<div style="height: 20px;"></div>

#### Measurement Points 

<div style = "display: flex; gap: 20px;">
<div><strong>T2</strong><br></div>
<div><strong>T5</strong><br></div>
<div><strong>T8</strong><br></div>
</div>


<div style="height: 10px;"></div>


**Sample Size**

<div style="border: 2px solid black; padding-left: 5px;">N = 1780, n = 7964</div>  

<div style="margin-left:5px;">
N = number of participants, n = number of data points across measurement occasions
</div>
<div style="height: 20px;"></div>

```{r echo=FALSE}
library(ggplot2)

set.seed(1234)
TPs <- c("T2", "T5","T8")
N = sample(800:1780, length(TPs), replace = TRUE)
data = data.frame(TPs = factor(TPs, levels = TPs, ordered = TRUE), N)

ggplot(data, aes(TPs, N)) + 
  theme_minimal() + 
  geom_bar(stat = "identity", color = "#B02F2C", fill = "#B02F2C") + 
  labs(x = "Measurement Occasion", y = "Observations")
```
<button>Download Data</button>

</div><!--First Column -->



<div class="column">

### Construct: Age satisfaction

#### English

**Intro**: For the last 3 months I have been thinking at work that...  
**Text**: things are getting worse as I get older.  <br>
**Scale**:  

- 1 = strongly disagree
- 2 = disagree
- 3 = somewhat disagree
- 4 = neither agree nor disagree
- 5 = somewhat agree
- 6 = agree
- 7 = strongly agree 

**Citation**: Lawton, M. P. (1975). The Philadelphia Geriatric Center Morale Scale: A revision. *Journal of Gerontology, 30*, 85–89.https://doi.org/10.1093/geronj/30.1.85 

#### German

**Intro**: In den letzten 3 Monaten habe ich bei der Arbeit gedacht, dass... <br>
**Text**: ...die Dinge schlechter werden je älter ich werde. <br>
**Scale**:  

- 1 = trifft überhaupt nicht zu 
- 2 = trifft nicht zu 
- 3 = trifft wenig zu 
- 4 = trifft teilweise zu 
- 5 = trifft ziemlich zu 
- 6 = trifft zu
- 7 = trifft voll und ganz zu 

**Citation**: Self-translated

#### Measured at 
<div class ="flex-container">

```{r, results='asis', echo=FALSE}
MPs = as.numeric(stringr::str_extract_all(string = TPs, pattern = "\\d+"))
for(i in 1:54) {
  if(i %in% MPs) {
    cat(paste0("<div class=\"measured\">T", i, "</div>", "\n"))
  } else {
    cat(paste0("<div>T", i, "</div>", "\n"))
  }
}
```



</div><!-- flex-container -->

</div><!--Second Column -->
</div><!--"Row"-->


## Example 2 - Three Timepoints {-}  

<div class="row">
<div class="column">
<input
type="text"
placeholder="Search"
/>

<div style="border: 2px solid black; padding: 0 20px; margin-bottom: 20px; list-style-position: outside;">
<li>T1 (12/2019)</li>
<ul>
<li>Demographics</li>
<li>Job Attitudes</li>
<ul>
<li>Job Engagement</li>
<li>Job Satisfaction</li>
<li>Turnover Intentions</li>
<li>Retirement Intentions</li>
<ul>
<li style="background:AliceBlue;">retire1: I expected to begin collecting a pension in the near future</li>
<li>retire2: I was thinking about retiring in the near future</li>
<li>retire3: I was planning to retire in the near future</li>
<li>retire4: I was expecting to retire in the near futre</li>
</ul>
</ul>
</ul>
<li>T2 (03/2020)</li>
<ul>
<li>Demographics</li>
<li>Job Attitudes</li>
<ul>
<li>Job Engagement</li>
<li>Job Satisfaction</li>
<li>Turnover Intentions</li>
<li>Retirement Intentions</li>
</ul>
</ul>
</ul>
<li>T3 (04/2020)</li>
<ul>
<li>Demographics</li>
<li>Job Attitudes</li>
<ul>
<li>Job Engagement</li>
<li>Job Satisfaction</li>
<li>Turnover Intentions</li>
<li>Retirement Intentions</li>
<ul>
</ul>
</li>

</ul>
</li>

</ul>

</div>



#### Selection

<div style="border: 2px solid black; padding-left: 5px;">retire1</div>  

<div style="height: 20px;"></div>

#### Measurement Points 

<div style = "display: flex; gap: 20px;">
<div><strong>T1</strong><br></div>
<div><strong>T2</strong><br></div>
<div><strong>T3</strong><br></div>
</div>


<div style="height: 10px;"></div>

**Sample Size**

<div style="border: 2px solid black; padding-left: 5px;">N = 1780, n = 7964</div>  

<div style="margin-left:5px;">
N = number of participants, n = number of data points across measurement occasions
</div>
<div style="height: 20px;"></div>


```{r echo=FALSE}
library(ggplot2)

set.seed(1234)
TPs <- c("T1","T2", "T3")
N = sample(800:1780, length(TPs), replace = TRUE)
data = data.frame(TPs = factor(TPs, levels = TPs, ordered = TRUE), N)

ggplot(data, aes(TPs, N)) + 
  theme_minimal() + 
  geom_bar(stat = "identity", color = "#B02F2C", fill = "#B02F2C") + 
  labs(x = "Measurement Occasion", y = "Observations")
```

<button>Download Data</button>

</div><!--First Column -->




<div class="column">
### Construct: Turnover Intentions  

#### English

**Intro**: In the last 3 months/4 weeks...<br>
**Text**: ...I expected to begin collecting a pension in the near future. <br>
**Scale**:  

- 1 = strongly disagree 
- 2 = disagree
- 3 = somewhat disagree 
- 4 = neither agree nor disagree 
- 5 = somewhat agree 
- 6 = agree 
- 7 = strongly agree 

**Citation**: Adams, G. A., & Beehr, T. A. (1998). Turnover and retirement: A comparison of their similarities and differences. *Personnel Psychology, 51*(3), 643–665. https://doi.org/10.1111/j.1744-6570.1998.tb00255.x

#### German

**Intro**: In den letzten 3 Monaten/4 Wochen...<br>
**Text**: ...rechnete ich damit, bald Rente zu erhalten. <br>
**Scale**:  

- 1 = trifft überhaupt nicht zu
- 2 = trifft nicht zu
- 3 = trifft wenig zu
- 4 = trifft teilweise zu
- 5 = trifft ziemlich zu
- 6 = trifft zu
- 7 = trifft voll und ganz zu

**Citation**: Self-translated

#### Measured at 
<div class ="flex-container">

```{r, results='asis', echo=FALSE}
MPs = as.numeric(stringr::str_extract_all(string = TPs, pattern = "\\d+"))
for(i in 1:54) {
  if(i %in% MPs) {
    cat(paste0("<div class=\"measured\">T", i, "</div>", "\n"))
  } else {
    cat(paste0("<div>T", i, "</div>", "\n"))
  }
}
```



</div><!-- flex-container -->


</div><!--Second Column -->



</div><!--"Row"-->
